\begin{rubric}{Professional experience}
\subrubric{Business Transformation: Crate\&Barrel - Chicago USA}
\entry*[04/2013 - today] \textbf{Director: Technology}\newline
\textax{Content:} 
Overall responsibility for IT-Infrastructure, Operations and Security (Department Head 40+ employees/ Budget 15 Mil. USD/Year): Datacenter (24/7 Operations), Warehouse- and Distributions Network, all retail locations; Workstations, Support, Server/Storage (IBM Power 7+ \& X86, Win/AIX/Linux/ISeries), Cloud (aws, google), Network (WAN, LAN, Wi-Fi) und Telco. Project management for all transformation projects regarding infrastructure.

\textax{Role:} 
Turnaroundmanagement IT-Infrastructure, Consultant to CTO \& CIO: Formulating, driving and developing an infrastructure strategy. Consolidation, virtualization and outsourcing: Selection of technologie, intergration partner and the model of operation. Development of a comprehensive security/risk program: identify, protect, detect, response and recover.

\entry*[10/2011 - 03/2013] \textbf{Director: Portfolio Management und Governance}\newline
\textax{Content:} 
Design and execution of all investment and program managment processes (regular steering meeting with C-level-Management). Portfolio Management of all projects for the business (ca. 40 Mil. USD/year). Projectmanagement for transformation projects.\axelvspace

\textax{Role:} 
Turnaroundmanagement Business and IT, Consultant to CTO \& CEO: Formulating, driving and developing a transformation strategy (from custom to package \& cloud and outsourcing), vendor \& integrator selection, program managment, project management, change management.\newline

\pagebreak
\subrubric{IT/Logistics: Ottogroup [01/2005-10/2011]}
\entry*[08/2009 - 10/2011] \textbf{Head of Department: Corporate IT / Governance}\newline
\textax{Content:} 
Responsibility for the governance instruments of the Ottogroup: project initialization, project definition, project closure and post mortem analysis, establishment and execution of the executive governance board.\axelvspace

\textax{Role:} 
Quality Gate, sign off of all IT projects of the european retail operation of the Ottogroup. Project review based for completeness, plausibility, business case and alignment with the IT strategy. CIO taskforce member to drive change management activities. Establishment of a segregation between IT solution provider and the Corporate IT.

\entry*[08/2006 - 07/2009] \textbf{Head of Department: Order processing and invoicing}\newline
\textax{Content:} 
Responsible for business processes from order entry to shipping: availability, allocation , shipment building, optimization, capacity management, invoicing, warehouse management for 11 locations in europe.\axelvspace

\textax{Role:} 
Leader for 40 staff in 3 locations. Managment of integrators and vendors, responsible for 7-8 Mio EUR/year project volumen.

\entry*[01/2005 - 07/2006] \textbf{Lead developer: Masterdata systems}\newline
\textax{Content:} 
Online connection to hostsystem with J2EE architecture for logistical processes like: sorting and allocation of returns.\axelvspace

\textax{Role:} 
Lead developer for 15 staff, Release management for 4000 person days releases.

\subrubric{Consulting: Accenture [12/2001-12/2004]}
\entry*[10/2003 - 12/2004] \textbf{Investment Banking: Securities Processing Solution}\newline
\textax{Projekt:} 
Functional/technical design, implementation and test of a trade enrichment system for institutional trading for a major german bank.\axelvspace

\textax{Role:} 
As technical lead of 9 developers I was responsible for technical design and implementation of various functional elements of the core system e.g. trade management for brokers and the backoffice. 
%\axelvspace
%\textax{Technische Architektur:}
%Java, ant, CVS, IBM Enterprise Application Integration Middleware, Bea Weblogic J2EE Application Server, Oracle Toplink Persistenz, Oracle 9i Datenbank

\entry*[07/2003 - 10/2003] \textbf{Capital Markets: Transatlantic Future Trading and Clearing Solution}\newline
\textax{Project:} 
Developing the functional blueprint of a Global Clearing Solution: Specifically a transatlantic clearing link for financial instruments traded in the US and Europe. The major difficulty was the alignment of trading and clearing infrastructures and legal/regulatory requirements.

\textax{Role:} 
As part of the Business Architects Office I conducted a functional comparison of the current trading and clearing infrastructures, developed parts of the functional design for the clearing link and established project/issue management processes.

\entry*[12/2001 - 06/2003] \textbf{Capital Markets: Central Counterparty for Equities (CCP)}\newline
\textax{Project:} 
A stock exchange already providing central counterparty services in the derivatives, bonds and repos market entered the cash \& equities services market. To cover the assumed market risk, net risk positions are determined for each participant and associated collateral requirements are calculated and reported to members. 

\textax{Role:} 
I was responsible for creation of technical designs based on functional requirements for the Clearing Supervision user interface as part of the development and architecture teams.
After production start I was leading the user interface team. Main tasks were planning, scheduling and tracking fixits and enhancements for the production environment. Major responsibility was to ensure smooth delivery processes and scope control. I was coaching and facilitating the client lead in performing status reporting,
estimations and resource planning.

\subrubric{Logistic: Otto Versand / www.otto.de}

\entry*[01/2001 - 10/2001] \textbf{Software Development: Warehouse Management}\newline

\textax{Project:} 
Development of warehouse management software for a distributed system in a heterogenic (Windows, Linux, Solaris) environment.

\textax{Role:} 
I was programming end-of-day processes for ERP Software and was in charge of reassuring quality of processes via hands-on check in the warehouse with experience warehouse staff.

%\subrubric{Public Services: City of Wedel}
%\entry*[09/1997 - 05/2001] \textbf{Teaching: Adult Evening Classes}\newline

%\textax{Project:}
%Basic Information Technology training. The majority of participants came from specific groups of %society (unemployed, elderly population) and had no or little information technology contact prior %attenting the classes.

%\textax{Role:} 
%I was in charge of preparing and conducting the training for groups of 16 people.

%\subrubric{Software Development: iXL Enterprises}
%\entry*[06/1999 - 10/1999] \textbf{Travel: Transactional Website Launch}\newline
%\textax{Project:} 
%Launch of a travel agent transactional website. 

\textax{Role:} 
I was in charge of the technical preparation of the website launch: organising and installing the hard and software, development of components to proceed bookings and handle email notifications using a code generation framework.

\subrubric{Banking: Vereins- und Westbank / www.vuw.de}
\entry*[06/1997 - 05/1999] \textbf{Controlling \& Support:}\newline
\textax{Project:} 
Internal controlling, reporting and financial reporting for 180 bank branches in the north of Germany. (9/1998 - 05/1999)
1st and 2nd level support user help desk (6/1997 - 09/1998)

\textax{Role:} 
As part of a team I was in charge of conducting the monthly profit centre reporting and benchmarking. Addionally I was in charge of implementing new reports and driving the development of a paperless reporting system. 
I was part of the call centre team. Beyond the call centre I was developing small software tools to undertake standard organisational tasks. 

\sloppy
\end{rubric}
